---
title: "DAhw_1"
author: "Lin,Pei Chen"
date: "2023-02-21"
output: html_document
--
Q.11
```{r}
library(ggplot2)
library(cowplot)
library(showtext)
```
create dice function
```{r}
dice<-function(x){
  z <- replicate(1000, mean(sample(1:6,x, replace = TRUE)))
  return(z)
}
```
simulate the number of dice for 1000 times
```{r}
twodice<-dice(2)
threedice<-dice(3)
fourdice<-dice(4)
fivedice<-dice(5)
```
plot the four histograms 
```{r}
plot.two<-ggplot(data.frame(x = twodice), aes(x)) +
  geom_histogram(bins = 25, fill = "skyblue4", alpha = 0.5) +
  labs(title = "2 Dice") +
  xlab("Num") +
  ylab("Prob")+
  scale_x_continuous(breaks=c(1,2,3,4,5,6),labels = c("1","2","3","4","5","6"))+
  scale_y_continuous(labels = scales::number_format(scale= 0.001))+
  theme(plot.title=element_text(hjust = 0.5,face="bold"))

plot.three<-ggplot(data.frame(x = threedice), aes(x)) +
  geom_histogram(bins = 50, fill = "skyblue4", alpha = 0.5) +
  labs(title = "3 Dice") +
  xlab("Num") +
  ylab("Prob")+
  scale_x_continuous(breaks=c(1,2,3,4,5,6),labels = c("1","2","3","4","5","6"))+
  scale_y_continuous(labels = scales::number_format(scale= 0.001))+
  theme(plot.title=element_text(hjust = 0.5,face="bold"))

plot.four<-ggplot(data.frame(x = fourdice), aes(x)) +
  geom_histogram(bins = 100, fill = "skyblue4", alpha = 0.5) +
  labs(title = "4 Dice") +
  xlab("Num") +
  ylab("Prob")+
  scale_x_continuous(breaks=c(1,2,3,4,5,6),labels = c("1","2","3","4","5","6"))+
  scale_y_continuous(labels = scales::number_format(scale= 0.001))+
  theme(plot.title=element_text(hjust = 0.5,face="bold"))

plot.five<-ggplot(data.frame(x = fivedice), aes(x)) +
  geom_histogram(bins = 150, fill = "skyblue4", alpha = 0.5) +
  labs(title = "5 Dice") +
  xlab("Num") +
  ylab("Prob")+
  scale_x_continuous(breaks=c(1,2,3,4,5,6),labels = c("1","2","3","4","5","6"))+
  scale_y_continuous(labels = scales::number_format(scale= 0.001))+
  theme(plot.title=element_text(hjust = 0.5,face="bold"))

plot<-ggdraw()+
  draw_plot(plot.two,0,0.5,0.5,0.5)+
  draw_plot(plot.four,0,0,0.5,0.5)+
  draw_plot(plot.three,0.5,0.5,0.5,0.5)+
  draw_plot(plot.five,0.5,0,0.5,0.5)
print(plot)
```

Q.12
```{r}
library(ggplot2)
```
create pokercard function
```{r}
pokercard<-function(x){
  z<-data.frame(face=rep(c(2:10,"J","Q","K","A"),4*x),hs=rep(c("Spades","Diamonds","Hearts","Clubs"),each=13)) 
  return(z)
}
```
shuffle function
```{r}
shuffle<-function(){
  copypkp<-pkp 
  random<-sample(c(1:nrow(pkp)),size=nrow(pkp)) 
  for (i in 1:nrow(pkp)) { 
    assign("copypkp",copypkp[random,],envir = globalenv()) 
  }
}
```
set x for the deck of cards and y for the number of steps for face cards 
```{r}
Game<-function(x,y){
  pkp<<-pokercard(x)
  copypkp<<-pkp 
  #licensing card
  assign("copypkp",copypkp[-1,],envir = globalenv())
  #paly 10000 times
  #calculate the numbers of the first 10 cards reach the same card
  Card_prob<-0
  for(a in 1:10000){
    shuffle()
    Card_data<-c()
    #pick a card in first 10 cards
    for(z in 1:10){
      card<-copypkp[z,]
      new_index<- which(rownames(copypkp)==rownames(card))
      row_index<-new_index
      #go to the next card
      for(i in 2:52*x){
        if (row_index<=new_index){
          for(j in 2:10){
            if(card$face=="A"){
              new_index<-row_index+1
              break
            }else if(card$face=="J"){
              new_index<-row_index+y
              break
            }else if(card$face=="Q"){
              new_index<-row_index+y
              break
            }else if(card$face=="K"){
              new_index<-row_index+y
              break
            }else if (as.numeric(card$face)==j){
              new_index<-row_index+j
              break
            }
          }
          if(new_index>52*x){
            break
          }
          else{
            row_index<-new_index
            card<-copypkp[row_index,]
          }
        }
      }
      Card_data<-c(Card_data,row_index)
    }
    num<-table(Card_data)
    ifelse(num/10==1,Card_prob<-Card_prob+1,Card_prob)
  }
  return(Card_prob/10000)
}
```
save the results for each different parameter
```{r}
result_df<-data.frame(x=numeric(),y=numeric(),result=numeric())
for(i in 1:2){
  for(j in seq(from=1,to=9,by=2)){
    x<-i
    y<-j
    result<-Game(i,j)
    result_df<-rbind(result_df,data.frame(x=x,y=y,result=result))
  }
}
print(result_df)

```
From the above result,we can find out that the larger number of steps comes with a higher probability.If we use two decks to simulate the game,we can find out the same pattern but with a higher probability.
```{r}
ggplot(result_df, aes(x = paste(x, y, sep = ","), y = result,fill=factor(x))) +
  geom_col() +
  labs(x = "deck of cards,# of steps for face cards", y = "Probability")+
  scale_fill_manual(values=c("cadetblue","navajowhite4"))
```

